Spatial Reasoning and Statistical Graphics

### 2014-12-15 Paper/Draft1/TestingVisualAptitude.Rnw
grammar

\newtext{The lineup protocol~\cite{hofmann2012graphical,wickham2010graphical, buja2009statistical} is introducing a testing framework that allows to quantify the significance of graphical findings with the same mathematical rigor as conventional hypothesis tests. }

>>>>

\newtext{The lineup protocol~\cite{hofmann2012graphical,wickham2010graphical, buja2009statistical} is a testing framework that allows us to quantify the significance of graphical findings with the same mathematical rigor as conventional hypothesis tests. }
